DNSKEY Management

### 2012-12-04 paper/paper.tex
Spellcheck

\twocolumn[
\maketitle
\begin{onecolabstract}
  In this paper we recapitutale the current deployment status of
  DNSSEC and go into the main issues when managing its keys. It
  outlines the paper ``Interadministrative Challenges in Managing
  DNSKEYs'' \cite{Osterweil09} and updates some of its contents
  especially with respect to the signing of the root zone on July
  15, 2012. We will see that DNSSEC penetration in the Internet's
  zones is still low but that the necessary foundations have been lain
  for full deployment.
\end{onecolabstract}
\vspace{\baselineskip}
]

@@

In this paper we will first remind of the prinicpal necessary
operations for key management in DNSSEC. Then we will give the reader
an overview of the current status of DNSSEC deployment in the Internet
to put the in-detail discussion about key management into the right
context.

@@

\subsection{Operations}
In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader. This is by no means
intended to give an introduction to DNSSEC but rather to remind the
reader about specific details particularily relevant to this paper.

@@

\paragraph{Key Rollover} RFC4641 \cite{RFC4641} suggests that the DNSKEY
records for a zone should be changed somewhere between once every week
up to once every month. While the detailed rollover procedure is
irrelevant here, it is important to know, that the parent zone has to
update the its DS record.

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the internet namespace, three entities can generally be considered:

@@

The entities behind the three R's are the exact same wether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like IP addresses or billing data actually changed.

@@

\subsubsection{Single administrative domain}
Basically, once an organisation has its main domain signed, it is relatively easy for any sub-entity within said organisation to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key roll-over: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.

>>>>

\twocolumn[
\maketitle
\begin{onecolabstract}
  In this paper we recapitulate the current deployment status of
  DNSSEC and go into the main issues when managing its keys. It
  outlines the paper ``Interadministrative Challenges in Managing
  DNSKEYs'' \cite{Osterweil09} and updates some of its contents
  especially with respect to the signing of the root zone on July
  15, 2012. We will see that DNSSEC penetration in the Internet's
  zones is still low but that the necessary foundations have been lain
  for full deployment.
\end{onecolabstract}
\vspace{\baselineskip}
]

@@

In this paper we will first remind of the principal necessary
operations for key management in DNSSEC. Then we will give the reader
an overview of the current status of DNSSEC deployment in the Internet
to put the in-detail discussion about key management into the right
context.

@@

\subsection{Operations}
In the following, every necessary operation for key management in
DNSSEC is described as a reminder to the reader. This is by no means
intended to give an introduction to DNSSEC but rather to remind the
reader about specific details particularly relevant to this paper.

@@

\paragraph{Key Rollover} RFC4641 \cite{RFC4641} suggests that the DNSKEY
records for a zone should be changed somewhere between once every week
up to once every month. While the detailed rollover procedure is
irrelevant here, it is important to know, that the parent zone has to
update its DS record.

@@

\section{Operations\wbjp}
This section covers the issues and quirks related to the management of DNSSEC.
\subsection{3Rs}
%% Talk about EPP or push burden to Case-Study
Regarding the management of the Internet namespace, three entities can generally be considered:

@@

The entities behind the three R's are the exact same whether DNSSEC is used or not, but DNSSEC modifies the relations among them: e.g., DNSKEY updates will now also require communication between the three R's, even if no practical information like IP addresses or billing data actually changed.

@@

\subsubsection{Single administrative domain}
Basically, once an organization has its main domain signed, it is relatively easy for any sub-entity within said organization to get a sub-domain signed, and to coordinate any operations relative to DNSSEC like key rollover: staying with our EPFL example, it can suffice to contact the IT-department and discuss about the procedure with them\footnote{EPFL does not actually use DNSSEC, but we use the school as an example for the sake of simplicity.}. The bottom line is that it is relatively easy to handle the additional work and information updates required by DNSSEC as long as every concerned party lies within the same organization.
\subsubsection{Multiple administrative domain}
DNSSEC's true challenges arise when we begin to consider several administrative entities (the three R's, mainly). As stated earlier, once the \verb|epfl.ch| zone is signed it is easy for the school to sign \verb|www.epfl.ch|. However, if the domain to be signed was \verb|epfl.ch| or \verb|epfl.ae|, the school would have to deal with the entity or entities managing the TLD's (\verb|ch.| managed by Switch or \verb|ae.|\footnote{epfl.ae has been registered at 'Instra Corporation Pty Ltd', a registrar for the ae.}, respectively), which will have they own terms and conditions, which might very well be different among different registrars and TLD's.
